Technical Report

### 2018-06-21 fully-abstract-comp/technical-report.tex
Fix some TODOs.
FTLR register file safety case done.

\[
  \lrvtrusted[\square,(\ta,\stkb,\gsigrets,\gsigcloss)](W) =
  \begin{array}[t]{l}
    \lrv(W)\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \begin{array}{l}
      \exists r \in \dom(\pwheap) \ldotp \\
      \quad \pwheap(r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)} \wedge\\
      \quad \dom(\code) \subseteq \ta \wedge [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets\cup\sigcloss) \wedge\\
      \quad \sigrets \subseteq \gsigrets \wedge \sigcloss \subseteq \gsigcloss
    \end{array}
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\normal),\baddr,\eaddr,\aaddr)},\\ ((\perm,\normal),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \perm \sqsubseteq \rx \wedge \\
      \gc = (\ta,\stkb,\gsigrets,\gsigcloss)  \wedge \\
      {} [\baddr,\eaddr] \subseteq \ta \wedge\\
      \npair{[\baddr,\eaddr]} \in \xReadCond[\square,\gc]{W} 
    \end{array}
    \right\}
  \end{array}
\]

@@

\begin{multline*}
  H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_,\gsigrets,\gsigcloss) \; \hat{W} =\\
  \left\{\npair{(\code,\code)} \middle|
    \begin{array}{l}
    \dom(\code) = [\aaddr,\baddr] \wedge \\
      (\dom(\code) \subseteq \ta \wedge \sigrets \subseteq \gsigrets \wedge \trust = \trusted) \vee \\
      \quad (\dom(\code)\mathrel{\#} \ta \wedge \sigrets = \emptyset \wedge \trust =\untrusted) \wedge \\
      \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code \wedge\\
      \forall a \in \dom(\code)\ldotp\\
      \quad\npair{(\code(a),\code(a))} \in \lrvg{\trust}(\purePart{\xi(\hat{W})})
    \end{array}
  \right\}
\end{multline*}

@@

\begin{definition}[Reasonable configuration]
  \label{def:reasonable-conf}
  We say that an execution configuration $\Phi$ is reasonable up to $n$ steps
  iff for all $n' \le n$:
  \begin{itemize}
  \item \emph{Guarantee stack base address before call} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\Phi'$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$
      for some $\src{r_1}$ and $\src{r_2}$
    \item $0 < i \le n'$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi'}(\src{r_\stk}) =
      \src{\stkptr{\_,\stkb,\eaddr_\stk,\aaddr_\stk}}$
    \item $r_1 \neq \rtmp{1}$
    \item $\Phi'(\pcreg) + \calllen$ and $\Phi'(\rstk)$ behaves reasonably up to
      $n'-i$ steps
    \end{itemize}
  \item \emph{Use return seals only for calls, use closure seals appropriately} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item i > 0
    \item $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi'}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$
      and $\sigma \in \gsigrets$
    \item $\sigma \in \gsigcloss$ and one of the following holds:
      \begin{itemize}
      \item $\exec{\Phi'(r_2)}$ and $\Phi'(r_2)$ behaves reasonably up to $n$ steps.
      \item $\nonExec{\Phi'(r_2)}$ and $\Phi'(r_2)$ is reasonable up to $n$ steps in memory $\Phi'.\ms$ and free stack $\Phi'.\ms_\stk$.
      \end{itemize}
    \end{itemize}
  \item \emph{Don't store private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then
    \item $0 < i \le n'$
    \end{itemize}
    Then $\Phi.\reg(r_2)$ is reasonable in memory $\Phi'.\mem$ up to $n'-i$ steps
  \item \emph{Don't leak private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi' \step \Phi''$
    \item $\src{\Phi'}$ is in $\ta$
    \item $\src{\Phi''}$ is not in $\ta$
    \item $0 < i \le n'$
    \end{itemize}
    Then $\Phi.\reg(r)$ is reasonable in memory $\Phi'.\mem$ up to $n'-i$ steps for
    all $r$ (including $\pcreg$)
  \end{itemize}  
\end{definition}

@@

\begin{lemma}
  \label{lem:codereg-Hsigma-not-lrv}
  If $\dom(\code) \subseteq \ta$,  $\sigrets \subseteq \gsigrets$, $\sigcloss \subseteq \gsigcloss$, $n > 0$ and $\sigma \in (\sigrets \uplus \sigcloss)$, then $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}.H_\sigma~ \sigma \not\nequal (\lrv \circ \xi)$.
\end{lemma}
\begin{proof}
  Consider the following two cases:
  \begin{itemize}
  \item $\sigma \in \sigrets$:

    In this case, we have that $\npair[0]{\left(\retptrd(\baddr,\eaddr),((\rw,\linear),\baddr,\eaddr,\baddr-1)\right)}$ is not in $\lrv(\xi(\hat{W}))$, but we can show that it is in $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}.H_\sigma~ \sigma~\hat{W}$ by taking a $\hat{W}$ such that the following hold:
    \begin{itemize}
    \item $\sigrets \subseteq \gsigrets$: assumption.
    \item $\dom(\code) \subseteq \ta$: assumption.
    \item $\exists r \in \addressable{\linear,\pwpriv[\xi(\hat{W})]}$ such that $\pwpriv[\xi(\hat{W})](r).H \nequal (\stareg[(\ms_S,\ms_T),(\ta,\stkb)]{\spao,\square}, \aaddr'+\calllen)$, $\dom(\ms_S) = \dom(\ms_T) = [\baddr,\eaddr]$, $\decInstr{\code([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$, $\code(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand \sigma = \sigma_b + \offsigma \in \sigrets$.
      It is not difficult to construct a $\hat{W}$ with a suitable $\spatialo$ region to satisfy these conditions. 
    \end{itemize}

@@

\begin{lemma}[Untrusted source values are reasonable]
  \label{lem:untrusted-source-values-are-reasonable}
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(w,\_)} \in \lrv(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$, $w$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
\end{lemma}
\begin{proof}
  Induction over $n$.
  For $n=0$ all words are reasonable.
  For $n>0$, we need to prove four implications:
  \begin{itemize}
  \item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$:

@@

    From the facts that $\pwheap[W_w](r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$, $\pwheap[W_w].H_\sigma~\sigma \nequal \lrv$, the disjointness of all the $R_{\var{seal}}(r)$, it follows that $r = r_\code$.
    However, this contradicts Lemma~\ref{lem:codereg-Hsigma-not-lrv}.

@@

\begin{lemma}[Untrusted register files are reasonable]
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(\reg_S,\_)} \in \lrr(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  \begin{itemize}
  \item $\reg_S(r)$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$ for all $r \not\in \{\pcreg\}$
  \item $\ms_S$, $\ms_\stk$ and $\stk$ are all disjoint
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove the three results separately:
  \begin{itemize}
  \item $\reg_S(r)$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$ for all $r \not\in \{\pcreg\}$:

@@

  By definition of $\lrvg{\trusted}$, it is clear that also $\npair{(w,w_T)} \in \lrv(W_w)$, except in the following two cases:
  \begin{itemize}
  \item
    \begin{itemize}
    \item $w = \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}}$
    \item $w_T = \seal{\sigma,\sigma_\baddr,\sigma_\eaddr}$ 
    \item $r \in \dom(\pwheap)$
    \item $\pwheap(r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$
    \item $\dom(\code) \subseteq \ta$ 
    \item $[\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets\cup\sigcloss)$ 
    \item $\sigrets \subseteq \gsigrets$
    \item $\sigcloss \subseteq \gsigcloss$
    \end{itemize}

@@

\begin{lemma}[permission-based conditions shrinkable]
  \label{lem:conds-shrinkable}
  \begin{itemize}
  \item If $\npair{A} \in \readCond{\lin,W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \readCond{\lin,W}$.
  \item If $\npair{A} \in \writeCond{\lin,W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \writeCond{\lin,W}$.
  \item If $\npair{A} \in \xReadCond{W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \xReadCond{W}$.
  \item If $\npair{A} \in \execCond{W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \execCond{W}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  Follows easily from the definitions.
  In the case for $\execCond$ where $\lin = \linear$, we have a partition of the world into $W = \oplus_{a \in A} W_a(a)$ that we need to convert into a partition $W = \oplus_{a \in A'} W_a'(a)$.
  It suffices construct new $W_a'$ by taking $W_a$ but adding $\oplus_{a\in(A\setminus A')}$ to an $W_a(a)$ for an arbitrary $a \in A'$ to make this work.
\end{proof}

>>>>

\[
  \lrvtrusted[\square,(\ta,\stkb,\gsigrets,\gsigcloss)](W) =
  \begin{array}[t]{l}
    \lrv(W)\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \begin{array}{l}
      \exists r \in \dom(\pwheap) \ldotp \\
      \quad \pwheap(r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb,\gsigrets,\gsigcloss)} \wedge\\
      \quad \dom(\code) \subseteq \ta \wedge [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets\cup\sigcloss) \wedge\\
      \quad \sigrets \subseteq \gsigrets \wedge \sigcloss \subseteq \gsigcloss
    \end{array}
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\normal),\baddr,\eaddr,\aaddr)},\\ ((\perm,\normal),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \perm \sqsubseteq \rx \wedge \\
      \gc = (\ta,\stkb,\gsigrets,\gsigcloss)  \wedge \\
      {} [\baddr,\eaddr] \subseteq \ta \wedge\\
      \npair{[\baddr,\eaddr]} \in \xReadCond[\square,\gc]{W} 
    \end{array}
    \right\}
  \end{array}
\]

\begin{lemma}[Untrusted is trusted]
  \label{lem:untrusted-subset-trust}
  \begin{itemize}
  \item $\lrvtrusted(W) \subseteq \lrv(W)$
  \item $\lrrtrusted(W) \subseteq \lrr(W)$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\begin{multline*}
  H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_,\gsigrets,\gsigcloss) \; \hat{W} =\\
  \left\{\npair{(\code,\code)} \middle|
    \begin{array}{l}
      ((\dom(\code) \subseteq \ta \wedge \sigrets \subseteq \gsigrets \wedge \trust = \trusted) \vee \\
      \quad (\dom(\code)\mathrel{\#} \ta \wedge \sigrets = \emptyset \wedge \trust =\untrusted)) \wedge \\
      \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code \wedge\\
      \forall a \in \dom(\code)\ldotp\\
      \quad\npair{(\code(a),\code(a))} \in \lrvg{\trust}(\purePart{\xi(\hat{W})})
    \end{array}
  \right\}
\end{multline*}

@@

\begin{definition}[Reasonable configuration]
  \label{def:reasonable-conf}
  We say that an execution configuration $\Phi$ is reasonable up to $n$ steps
  iff for all $n' \le n$:
  \begin{itemize}
  \item \emph{Guarantee stack base address before call} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\Phi'$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$
      for some $\src{r_1}$ and $\src{r_2}$
    \item $0 < i \le n'$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi'}(\src{r_\stk}) =
      \src{\stkptr{\_,\stkb,\eaddr_\stk,\aaddr_\stk}}$
    \item $r_1 \neq \rtmp{1}$
    \item $\Phi'(\pcreg) + \calllen$ behaves reasonably up to $n'-i$ steps
    \end{itemize}
  \item \emph{Use return seals only for calls, use closure seals appropriately} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item i > 0
    \item $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi'}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$
      and $\sigma \in \gsigrets$
    \item $\sigma \in \gsigcloss$ and one of the following holds:
      \begin{itemize}
      \item $\exec{\Phi'(r_2)}$ and $\Phi'(r_2)$ behaves reasonably up to $n$ steps.
      \item $\nonExec{\Phi'(r_2)}$ and $\Phi'(r_2)$ is reasonable up to $n$ steps in memory $\Phi'.\ms$ and free stack $\Phi'.\ms_\stk$.
      \end{itemize}
    \end{itemize}
  \item \emph{Don't store private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then
    \item $0 < i \le n'$
    \end{itemize}
    Then $\Phi.\reg(r_2)$ is reasonable in memory $\Phi'.\mem$ up to $n'-i$ steps
  \item \emph{Don't leak private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi' \step \Phi''$
    \item $\src{\Phi'}$ is in $\ta$
    \item $\src{\Phi''}$ is not in $\ta$
    \item $0 < i \le n'$
    \end{itemize}
    Then $\Phi.\reg(r)$ is reasonable in memory $\Phi'.\mem$ up to $n'-i$ steps for
    all $r$ (including $\pcreg$)
  \end{itemize}  
\end{definition}

@@

\begin{lemma}
  \label{lem:codereg-Hsigma-not-lrv}
  If $\dom(\code) \subseteq \ta$,  $\sigrets \subseteq \gsigrets$, $\sigcloss \subseteq \gsigcloss$, $n > 0$ and $\sigma \in (\sigrets \uplus \sigcloss)$, then $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb,\gsigrets,\gsigcloss)}.H_\sigma~ \sigma \not\nequal (\lrv \circ \xi)$.
\end{lemma}
\begin{proof}
  Consider the following two cases:
  \begin{itemize}
  \item $\sigma \in \sigrets$:

    In this case, we have that $\npair[0]{\left(\retptrd(\baddr,\eaddr),((\rw,\linear),\baddr,\eaddr,\baddr-1)\right)}$ is not in $\lrv(\xi(\hat{W}))$, but we can show that it is in $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb,\gsigrets,\gsigcloss)}.H_\sigma~ \sigma~\hat{W}$ by taking a $\hat{W}$ such that the following hold:
    \begin{itemize}
    \item $\sigrets \subseteq \gsigrets$: assumption.
    \item $\dom(\code) \subseteq \ta$: assumption.
    \item $\exists r \in \addressable{\linear,\pwpriv[\xi(\hat{W})]}$ such that $\pwpriv[\xi(\hat{W})](r).H \nequal (\stareg[(\ms_S,\ms_T),(\ta,\stkb)]{\spao,\square}, \aaddr'+\calllen)$, $\dom(\ms_S) = \dom(\ms_T) = [\baddr,\eaddr]$, $\decInstr{\code([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$, $\code(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand \sigma = \sigma_b + \offsigma \in \sigrets$.
      It is not difficult to construct a $\hat{W}$ with a suitable $\spatialo$ region to satisfy these conditions. 
    \end{itemize}

@@

\begin{lemma}[Untrusted source values are reasonable]
  \label{lem:untrusted-source-values-are-reasonable}
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(w,\_)} \in \lrv(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r_\code) \nequal \codereg{\gc}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$, $w$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
\end{lemma}
\begin{proof}
  Induction over $n$.
  For $n=0$ all words are reasonable.
  For $n>0$, we need to prove four implications:
  \begin{itemize}
  \item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$:

@@

    From the facts that $\pwheap[W_w](r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb,\gsigrets,\gsigcloss)}$, $\pwheap[W_w].H_\sigma~\sigma \nequal \lrv$, the disjointness of all the $R_{\var{seal}}(r)$, it follows that $r = r_\code$.
    However, this contradicts Lemma~\ref{lem:codereg-Hsigma-not-lrv}.

@@

\begin{lemma}[Untrusted register files are reasonable]
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(\reg_S,\_)} \in \lrr(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  \begin{itemize}
  \item $\reg_S(r)$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$ for all $r \not\in \{\pcreg\}$
  \item $\ms_S$, $\ms_\stk$ and $\stk$ are all disjoint
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove the three results separately:
  \begin{itemize}
  \item $\reg_S(r)$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$ for all $r \not\in \{\pcreg\}$:

@@

  By definition of $\lrvg{\trusted}$, it is clear that also $\npair{(w,w_T)} \in \lrv(W_w)$, except in the following two cases:
  \begin{itemize}
  \item
    \begin{itemize}
    \item $w = \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}}$
    \item $w_T = \seal{\sigma,\sigma_\baddr,\sigma_\eaddr}$ 
    \item $r \in \dom(\pwheap)$
    \item $\pwheap(r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb,\gsigrets,\gsigcloss)}$
    \item $\dom(\code) \subseteq \ta$ 
    \item $[\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets\cup\sigcloss)$ 
    \item $\sigrets \subseteq \gsigrets$
    \item $\sigcloss \subseteq \gsigcloss$
    \end{itemize}

@@

\begin{lemma}[permission-based conditions shrinkable]
  \label{lem:conds-shrinkable}
  \begin{itemize}
  \item If $\npair{A} \in \readCond{\lin,W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \readCond{\lin,W}$.
  \item If $\npair{A} \in \writeCond{\lin,W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \writeCond{\lin,W}$.
  \item If $\npair{A} \in \xReadCond{W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \xReadCond{W}$.
  \item If $\npair{A} \in \execCond{W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \execCond{W}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  Follows easily from the definitions.
  In the case for $\execCond{}$ where $\lin = \linear$, we have a partition of the world into $W = \oplus_{a \in A} W_a(a)$ that we need to convert into a partition $W = \oplus_{a \in A'} W_a'(a)$.
  It suffices construct new $W_a'$ by taking $W_a$ but adding $\oplus_{a\in(A\setminus A')}$ to an $W_a(a)$ for an arbitrary $a \in A'$ to make this work.
\end{proof}
